% ---------- %
% My Resume! %
% ---------- %

% ---------- PAGE SETUP ---------- %

\documentclass[letterpaper, 11pt]{article}
\usepackage{fontawesome5}
\usepackage{marvosym}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\input{glyphtounicode}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ---------- CUSTOM COMMANDS ---------- %

\newcommand{\resumeSchoolHeading}[4]{
  \vspace{-5pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeCompanyHeading}[3]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 $|$ #3
  \end{tabular*}
}

\newcommand{\resumePositionHeading}[2]{
  \vspace{-3pt}
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small#2}
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} $|$ \small\textit{#2} & #3
  \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSkillList}[2]{
  \textbf{#1:}{ #2 } \\ \vspace{1.5pt}
}

% ---------- RESUME! ---------- %

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Ivan David Diaz Sanchez} \\ \vspace{3pt}
  \small{
    \faPhone\space (425) 326-2657 $|$
    \Letter\space {diaz.ivan605@gmail.com} $|$
    \faLinkedin\space linkedin.com/in/ivandaviddiazsanchez
  }
\end{center}

% --------------- %
% Work Experience %
% --------------- %

\section{Work Experience}
\vspace{1pt}
\begin{itemize}[leftmargin=0.15in, label={}]

  % ------ %
  % Amazon %
  % ------ %

  \resumeCompanyHeading
    {Amazon}{Jun 2025 \textbf{--} Jan 2026}{Seattle, WA}

    % ---------------------------------------- %
    % Amazon Software Development Engineer III %
    % ---------------------------------------- %

    \resumePositionHeading
      {Software Development Engineer III (Contractor)}{Jun 2025 \textbf{--} Jan 2026}

      \begin{itemize}
        \resumeItem{Designed and implemented a scalable update orchestration system for Microsoft Office upgrades across Amazon-managed environments, ensuring security compliance and minimizing operational risk.}
        \resumeItem{Built a distributed monitoring and remediation service to detect configuration drift across internal environments and automatically reconcile inconsistencies.}
        \resumeItem{Architected and implemented a configurable release-discovery platform system to identify and find official software releases, streamlining processes in the environments. Additionally, developed an interface to support efficient testing and rapid iteration.}
      \end{itemize}\vspace{-5pt}


  % --------- %
  % Microsoft %
  % --------- %

  \resumeCompanyHeading
    {Microsoft Corporation}{Jul 2019 \textbf{--} Jan 2025}{Redmond, WA}

    % ------------------------------ %
    % Microsoft Software Engineer II %
    % ------------------------------ %

    \resumePositionHeading
      {Software Engineer II}{Sep 2021 \textbf{--} Jan 2025}

      \begin{itemize}
        \resumeItem{Contributed to the architecture and development of .NET Framework 4.8.1, including native ARM64 support, and collaborated closely with the Windows team to ensure seamless OS-level integration.}
        \resumeItem{Led runtime enhancements for .NET in Docker containers, enabling CPU resource configuration, developing ASP.NET Core composite images, and improving performance while reducing image size through data-driven benchmarking.}
        \resumeItem{Designed and implemented a new runtime API enabling dynamic entry assembly configuration, supporting launcher-based applications and cloud-hosted services deployed in Azure environments.}
      \end{itemize}\vspace{-5pt}

    % ----------------------------- %
    % Microsoft Software Engineer I %
    % ----------------------------- %

    \resumePositionHeading
      {Software Engineer}{Jul 2019 \textbf{--} Sep 2021}

      \begin{itemize}
        \resumeItem{Built infrastructure tooling to benchmark and analyze Garbage Collector performance across .NET Core and .NET Framework, supporting data-driven runtime optimizations.}
        \resumeItem{Improved build and test infrastructure for .NET Core, laying the groundwork for a unified runtime testing system and improving overall developer productivity.}
        \resumeItem{Provided initial fixes and enhancements to .NET Framework for ARM64, contributing to the eventual 4.8.1 release across all supported architectures.}
      \end{itemize}\vspace{-5pt}

  % ------ %
  % Oracle %
  % ------ %

  \resumeCompanyHeading
    {Oracle}{Jan 2017 \textbf{--} Jul 2019}{Zapopan, Jalisco, Mexico}

    % ---------------------------- %
    % Oracle Software Developer II %
    % ---------------------------- %

    \resumePositionHeading
      {Software Developer II}{Jan 2017 \textbf{--} Jul 2019}

      \begin{itemize}
        \resumeItem{Implemented new PL/SQL language features within the Oracle Database engine, including native large object management and specialized numerical operations.}
        \resumeItem{Designed and maintained comprehensive cross-language test frameworks ensuring functional parity and performance consistency between PL/SQL and SQL.}
        \resumeItem{Maintained and improved core Oracle Database packages with a focus on performance, correctness, and security.}
      \end{itemize}\vspace{-5pt}

\end{itemize}

% --------- %
% Education %
% --------- %

\section{Education}
\vspace{1pt}

\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeSchoolHeading
      {B.S. Computer Science and Technology}{GPA 3.6/4.0}
      {Instituto Tecnologico y de Estudios Superiores de Monterrey (ITESM)}{State of Mexico, Mexico}
\end{itemize}

% ----------- %
% Skills Sets %
% ----------- %

\section{Skills}
\vspace{1pt}

\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \resumeSkillList
      {Languages}
      {C, C++, C\#, Ruby, Python, JavaScript, SQL, PL/SQL, Bash, PowerShell, Elisp, Swift, Go, Julia, Lua}

    \resumeSkillList
      {Technologies}
      {AWS, Docker, Linux, .NET, Node.js, OpenAI API, Git, CI/CD, Distributed Systems, Software Architecture, Oracle, HTML/CSS, LaTeX, Emacs, Vim}

    \resumeSkillList
      {Methodologies and Paradigms}
      {Scrum, Agile Development, DevOps, Continuous Integration, Test-Driven Development, Object Oriented}
  }}
\end{itemize}


% --------------------- %
% Additional Experience %
% --------------------- %

\section{Additional Experience}
\vspace{1pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeItem{Completed hands-on coursework focused on building applications with the OpenAI API and Node.js, covering prompt design, API integration, response handling, and backend service workflows for LLM-powered systems.}
\end{itemize}

% -------- %
% Projects %
% -------- %

%% \section{Projects}
%% \vspace{1pt}
%% \begin{itemize}[leftmargin=0.15in, label={}]

%%   \resumeProjectHeading
%%     {Fie Bot}{Python, Discord API}{Nov 2024 \textbf{--} Feb 2025}

%%   \begin{itemize}
%%     \resumeItem{Developing a Discord bot using Python to provide utilities and mini-games to a server I have with some friends.}
%%     \resumeItem{Using this project for fun to also mentor one of my friends who is currently in the second half of his bachelor's in Computer Science.}
%%   \end{itemize}\vspace{-5pt}

%%   \resumeProjectHeading
%%     {Review Japanese App}{Python, Emacs Lisp}{Summer 2024}

%%     \begin{itemize}
%%       \resumeItem{Developed a small app on Python to help me practice Japanese vocabulary.}
%%       \resumeItem{Reads the words from custom dictionaries written in Emacs Lisp and Org-Mode, and uses Python to scramble and ask them via a prompt.}
%%       \resumeItem{Provides various forms of studying. It can ask for Kana/Kanji of word in English, or the English translation of a Japanese word in Kana/Kanji.}
%%     \end{itemize}\vspace{-5pt}
%% \end{itemize}

\end{document}
