% ---------- %
% My Resume! %
% ---------- %

% ---------- PAGE SETUP ---------- %

\documentclass[letterpaper, 11pt]{article}
\usepackage{fontawesome5}
\usepackage{marvosym}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\input{glyphtounicode}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ---------- CUSTOM COMMANDS ---------- %

\newcommand{\resumeSchoolHeading}[4]{
  \vspace{-5pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeCompanyHeading}[3]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 $|$ #3
  \end{tabular*}
}

\newcommand{\resumePositionHeading}[2]{
  \vspace{-3pt}
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small#2}
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} $|$ \small\textit{#2} & #3
  \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSkillList}[2]{
  \textbf{#1:}{ #2 } \\ \vspace{1.5pt}
}

% ---------- RESUME! ---------- %

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Ivan David Diaz Sanchez} \\ \vspace{3pt}
  \small{
    \faPhone\space (425) 326-2657 $|$
    \Letter\space {diaz.ivan605@gmail.com} $|$
    \faLinkedin\space linkedin.com/in/ivandaviddiazsanchez
  }
\end{center}

% --------------- %
% Work Experience %
% --------------- %

\section{Work Experience}
\vspace{1pt}
\begin{itemize}[leftmargin=0.15in, label={}]

  % ------ %
  % Amazon %
  % ------ %

  \resumeCompanyHeading
    {Amazon}{Jun 2025 \textbf{--} Jan 2026}{Seattle, WA}

    % ---------------------------------------- %
    % Amazon Software Development Engineer III %
    % ---------------------------------------- %

    \resumePositionHeading
      {Software Development Engineer III (Contractor)}{Jun 2025 \textbf{--} Jan 2026}

      \begin{itemize}
        \resumeItem{Designed and implemented a seamless Microsoft Office update and upgrade transition system, ensuring efficient enterprise-wide compliance and maintaining security standards across Amazon environments.}
        \resumeItem{Built an automated system drift detection and remediation job to monitor configuration inconsistencies across internal infrastructure, improving environment reliability and operational accuracy.}
        \resumeItem{Architected a configurable release-discovery system to identify official distributions of different software used by Amazon, reducing manual lookup efforts and accelerating deployment workflows; developed an accompanying test interface to streamline validation processes.}
      \end{itemize}\vspace{-5pt}


  % --------- %
  % Microsoft %
  % --------- %

  \resumeCompanyHeading
    {Microsoft Corporation}{Jul 2019 \textbf{--} Jan 2025}{Redmond, WA}

    % ------------------------------ %
    % Microsoft Software Engineer II %
    % ------------------------------ %

    \resumePositionHeading
      {Software Engineer II}{Sep 2021 \textbf{--} Jan 2025}

      \begin{itemize}
        \resumeItem{Shipped key components of .NET Framework 4.8.1, enabling native ARM64 support and porting high-impact features from .NET Core to modernize the runtime.}
        \resumeItem{Partnered with the Windows team to integrate the framework release seamlessly into the operating system, ensuring stability and compatibility at the OS level.}
        \resumeItem{Enhanced the .NET runtime for Docker containers by implementing configurable processor allocation, improving resource efficiency in containerized workloads.}
        \resumeItem{Led development of ASP.NET Core composite container images, conducting performance benchmarking across multiple scenarios to identify optimization opportunities. Reduced container image size while preserving performance gains, improving deployment efficiency and startup performance.}
        \resumeItem{Designed and implemented a new runtime API enabling dynamic entry assembly configuration, supporting advanced launcher applications and Azure-hosted service scenarios.}
      \end{itemize}\vspace{-5pt}

    % ----------------------------- %
    % Microsoft Software Engineer I %
    % ----------------------------- %

    \resumePositionHeading
      {Software Engineer}{Jul 2019 \textbf{--} Sep 2021}

      \begin{itemize}
        \resumeItem{Built performance benchmarking infrastructure to measure and analyze Garbage Collector behavior across .NET Core and .NET Framework, enabling data-driven runtime optimizations.}
        \resumeItem{Improved .NET Core build and test infrastructure, enhancing developer productivity and laying the groundwork for a unified runtime testing system.}
        \resumeItem{Delivered foundational ARM64 compatibility fixes for .NET Framework, contributing to the eventual cross-architecture release in version 4.8.1.}
      \end{itemize}\vspace{-5pt}

  % ------ %
  % Oracle %
  % ------ %

  \resumeCompanyHeading
    {Oracle}{Jan 2017 \textbf{--} Jul 2019}{Zapopan, Jalisco, Mexico}

    % ---------------------------- %
    % Oracle Software Developer II %
    % ---------------------------- %

    \resumePositionHeading
      {Software Developer II}{Jan 2017 \textbf{--} Jul 2019}

      \begin{itemize}
        \resumeItem{Developed new PL/SQL language features within the Oracle Database engine, including native Large Object (LOB) management and advanced numerical operations.}
        \resumeItem{Designed and maintained cross-language testing frameworks to ensure behavioral and performance parity between PL/SQL and SQL execution paths.}
        %% \resumeItem{Optimized and hardened Oracle Database packages, improving performance and strengthening security guarantees.}
      \end{itemize}\vspace{-5pt}

\end{itemize}

% --------- %
% Education %
% --------- %

\section{Education}
\vspace{1pt}

\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeSchoolHeading
      {B.S. Computer Science and Technology}{GPA 3.6/4.0}
      {Instituto Tecnologico y de Estudios Superiores de Monterrey (ITESM)}{State of Mexico, Mexico}
\end{itemize}

% ----------- %
% Skills Sets %
% ----------- %

\section{Skills}
\vspace{1pt}

\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \resumeSkillList
      {Languages}
      {C, C++, C\#, Ruby, Python, JavaScript, SQL, PL/SQL, Bash, PowerShell, Elisp, Swift, Go, Julia, Lua}

    \resumeSkillList
      {Technologies}
      {Git, .NET, Linux, AWS, Software Design, Software Infrastructure, Docker, OpenAI API, Node.js, HTML/CSS, LaTeX, Emacs, Vim, Oracle, Discord API}

    %% \resumeSkillList
    %%   {Testing \& Validation}
    %%   {Automated Testing, Test Infrastructure, System Validation, Performance Testing, Regression Testing, Benchmarking}

    \resumeSkillList
      {Methodologies and Paradigms}
      {Agile/Scrum, Object-Oriented Design, Test-Driven Development (TDD), DevOps, Continuous Integration (CI/CD), Relational Databases}
  }}
\end{itemize}

% --------------------- %
% Additional Experience %
% --------------------- %

\section{Additional Experience}
\vspace{1pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeItem{Completed hands-on coursework focused on building applications with the OpenAI API and Node.js, covering prompt design, API integration, response handling, and backend service workflows for LLM-powered systems.}
\end{itemize}

% -------- %
% Projects %
% -------- %

%% \section{Projects}
%% \vspace{1pt}
%% \begin{itemize}[leftmargin=0.15in, label={}]

%%   \resumeProjectHeading
%%     {Fie Bot}{Python, Discord API}{Nov 2024 \textbf{--} Feb 2025}

%%   \begin{itemize}
%%     \resumeItem{Developing a Discord bot using Python to provide utilities and mini-games to a server I have with some friends.}
%%     \resumeItem{Using this project for fun to also mentor one of my friends who is currently in the second half of his bachelor's in Computer Science.}
%%   \end{itemize}\vspace{-5pt}

%%   \resumeProjectHeading
%%     {Review Japanese App}{Python, Emacs Lisp}{Summer 2024}

%%     \begin{itemize}
%%       \resumeItem{Developed a small app on Python to help me practice Japanese vocabulary.}
%%       \resumeItem{Reads the words from custom dictionaries written in Emacs Lisp and Org-Mode, and uses Python to scramble and ask them via a prompt.}
%%       \resumeItem{Provides various forms of studying. It can ask for Kana/Kanji of word in English, or the English translation of a Japanese word in Kana/Kanji.}
%%     \end{itemize}\vspace{-5pt}
%% \end{itemize}

\end{document}
